\documentclass[10pt,english]{moderncv}

\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=2cm,bmargin=1cm,lmargin=1.5cm,rmargin=1.5cm}


\setcounter{secnumdepth}{0}
\setlength{\parskip}{10cm}
\setlength{\parindent}{0pt}
\usepackage{setspace}
\setstretch{1}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\newcommand{\noun}[1]{\textsc{#1}}


\def \fullcv {1}

% writing utilities

% comments and responses
%  -> use this comment to ask questions on what other wrote/answer questions with optional arguments (up to 4 answers)
\usepackage{xparse}
\usepackage{ifthen}
\DeclareDocumentCommand{\full}{m}{
\ifthenelse{\fullcv=1}{#1}{}
}




% adjust the page margins
%\usepackage[scale=0.87]{geometry}

\moderncvtheme[green]{classic}
% possible themes are "classic" and "casual"
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)

\setlength{\hintscolumnwidth}{2cm}

% required
\firstname{Juste}
% required
\familyname{Raimbault}

% optional, remove the line if not wanted
%\title{Curriculum Vitae}

% optional
% \address{street and number}{postcode city}
% '\\' adds a line break
%\address{13 rue du Four\vspace{1mm}}{75006 Paris, France}
\address{90 Tottenham Court Road\vspace{1mm}}{London W1T 4TJ, UK}
% optional
%\phone{+43(0)999 9999}
% optional
\mobile{+33648136295}
% optional
%\fax{+43(0)999 7777}
% optional
\email{juste.raimbault@polytechnique.edu}
% optional
\extrainfo{ORCID : 0000-0003-0768-9480}

% optional
% \photo[height]{name}
% 'height' is the height the picture is resized to
% 'name' is the name of the picture file
%\photo[90pt]{/Users/Juste/Pictures/moichat.jpg}

% optional
%\quote{Research Interests : Geosimulation Models; Model Exploration Algorithms; Corpus Mining}
%\quote{Complex Territorial Systems; Geosimulation; Quantitative Epistemology}

\makeatother

\usepackage{babel}
\begin{document}
\maketitle



%\vspace{1cm}


\section{Positions}

\cventry{Since January 2019}{Research Fellow}{CASA, UCL}{London}{UK}{\textit{Coupling land-use transport interaction models with microsimulation models}}

\cventry{March 2018-August 2019}{Post-doctoral Researcher}{Complex Systems Institute - UPS CNRS 3611 ISC-PIF}{Paris}{France}{Postdoc project: \textit{Extending methods to explore spatial simulation models}}







\section{Journal papers}

%\section{Selected publications}

\cvitem{}{Raimbault J., Broere J., Somveille M., Serna J.M., Strombom E. Moore C., Sugar L., Zhu B. (2019). A spatial agent based model for simulating and optimizing networked eco-industrial systems. \textit{Resources Conservation and Recycling.} In Press.}

\cvitem{}{Raimbault, J. \& Bergeaud, A. (2018). An Empirical Analysis of the Spatial Variability of Fuel Prices in the United States. \textit{Transportation Research Part A.} In Press.}

\cvitem{}{Raimbault, J. (2019). Second-order Control of Complex Systems with Correlated Synthetic Data. \textit{Complex Adaptive Systems Modeling.} In Press.}


\cvitem{}{Raimbault, J. (2019). Multi-dimensional Urban Network Percolation. \textit{Journal of Interdisciplinary Methodologies and Issues in Science.} In Press.}



\cvitem{}{Raimbault J., Cottineau C., Le Texier M., Le Nechet F. \& Reuillon R.
 (2019). Space Matters: extending sensitivity analysis to initial spatial conditions in geosimulation models. \textit{Journal of Artificial Societies and Social Simulation}, 22(4), 10.}

\cvitem{}{Banos A., Chasset P.-O., Commenges A. Cottineau C., Pumain D. \& Raimbault J. (2019). Empowering open science with reflexive and spatialised indicators. \textit{Environment and Planning B: Urban Analytics and City Science,} 2399808319870816.}



\cvitem{}{Raimbault, J. (2019). Exploration of an interdisciplinary scientific landscape. \textit{Scientometrics}, 119(2), 617-641.}

\cvitem{}{Raimbault, J. (2018). Calibration of a density-based model of urban morphogenesis. \textit{PloS one, 13(9), e0203516.}}

\cvitem{}{Raimbault, J. (2018). Indirect evidence of network effects in a system of cities. \textit{Environment and Planning B: Urban Analytics and City Science}, 2399808318774335.}

\cvitem{}{Bergeaud, A., Potiron, Y., \& Raimbault, J. (2017). Classifying patents based on their semantic content. \textit{PloS one}, 12(4), e0176310.}


\bigskip

\section{Book chapters}




\cvitem{}{Raimbault, J. (2019). An urban morphogenesis model capturing interactions between networks and territories. In \textit{The Mathematics of Urban Morphology (pp. 383-409)}. Birkhauser, Cham.}

\cvitem{}{Raimbault, J. (2019). Models for the co-evolution of cities and networks, \textit{forthcoming in Handbook on Cities and Networks, Rozenblat C., Neal Z., eds.} \href{https://arxiv.org/abs/1804.09430}{arXiv:1804.09430}}

\cvitem{}{Raimbault, J. (2018). Unveiling co-evolutionary patterns in systems of cities : systematic exploration of the SimpopNet model, \textit{forthcoming in Theories and models of urbanization. Pumain D., ed. Springer Lecture Notes in Morphogenesis.} \href{https://arxiv.org/abs/1809.00861}{arXiv:1809.00861}}

\cvitem{}{Raimbault, J. (2018). Relating complexities for the reflexive study of complex systems, \textit{forthcoming in Theories and models of urbanization. Pumain D., ed. Springer Lecture Notes in Morphogenesis.}}

\cvitem{}{Raimbault, J. (2018). Mutations of transportation networks in China, \textit{Medium Project e-book. Aveline N., ed.}}


\bigskip
\newpage

\section{Conference papers}

\cvitem{}{Raimbault, J. \& Perret, J. (2019).
Generating urban morphologies at large scales. \textit{The 2019 Conference on Artificial Life 2019 NO. 31}, 179-186.}

%\cvitem{}{Raimbault, J. (2019). Espace et complexit{\'e}s des syst{\`e}mes territoriaux. forthcoming in \textit{Actes des Journ{\'e}es de Rochebrune 2019.}}

%\cvitem{}{Raimbault, J. (2018). Mod{\'e}lisation des interactions entre r{\'e}seaux de transport et territoires : une approche par la co-{\'e}volution. forthcoming in \textit{Actes des Journ{\'e}es Pacte-Citeres.}}
% TODO arxiv trad en

\cvitem{}{Raimbault, J. (2017). An applied knowledge framework to study complex systems, \textit{Complex Systems Design \& Management} (pp.31-45). \href{https://arxiv.org/abs/1706.09244}{arXiv:1706.09244}}



\cvitem{}{Raimbault, J. (2017). Identification de causalit{\'e}s dans des donn{\'e}es spatio-temporelles, Sageo 2017 Proceedings. \href{https://arxiv.org/abs/1709.08684}{arXiv:1709.08684 (English translation)}}


\cvitem{}{Raimbault, J. (2017). A Discrepancy-Based Framework to Compare Robustness Between Multi-attribute Evaluations. In \textit{Complex Systems Design \& Management} (pp. 141-154), Springer.}



\cvitem{}{Raimbault, J. (2017). Investigating the empirical existence of static user equilibrium. \textit{Transportation Research Procedia}, 22, 450-458.}



\cvitem{}{Raimbault, J. (2017). Models coupling urban growth and transportation network growth: An algorithmic systematic review approach. \textit{Plurimondi}, (17), \textit{ECTQG 2015 Proceedings}. \href{https://arxiv.org/abs/1605.08888}{arXiv:1605.08888}}


\cvitem{}{Raimbault, J. (2014). User-Based Solutions for Increasing Level of Service in Bike-Sharing Transportation Systems. In \textit{Complex Systems Design \& Management} (pp. 31-44), Springer. \textit{\textbf{Best Student Paper Award at CSDM 2014.}}}

\cvitem{}{Raimbault, J., Banos, A. \& Doursat, R. (2014) A Hybrid Network/Grid Model of Urban Morphogenesis and Optimization. \textit{Proceedings of the 4th International Conference on Complex Systems and Applications} (ICCSA 2014), June 23-26, 2014, Universit{\'e} de Normandie, Le Havre, France; M. A. Aziz-Alaoui, C. Bertelle, X. Z. Liu, D. Olivier, eds.: pp. 51-60.}



%\newpage



\section{Communications}

\cvitem{}{A multi-scalar model for systems of cities, \textit{Conference on Complex Systems 2019, Singapore, Oct. 2019.}}

% TODO jig

% TODO TheoQuant

%\cvitem{}{Des syst{\`e}mes naturels aux syst{\`e}mes urbains: g{\'e}n{\'e}ration de r{\'e}seaux de transport optimaux par mod{\`e}le slime-mould, \textit{poster at Biomim'expo 2018, Paris, Oct. 2018.}}

\cvitem{}{A multi-dimensional percolation approach to characterize sustainable mega-city regions, \textit{MARAMI 2018, Avignon, Oct. 2018.}}

\cvitem{}{A systematic comparison of interaction models for systems of cities, \textit{Conference on Complex Systems 2018, Thessaloniki, Sept. 2018.}}

\cvitem{}{Extracting knowledge from simulation models: trends and perspectives from the viewpoint of quantitative geography, \textit{Conference on Complex Systems 2018, Thessaloniki, Sept. 2018.}}


\cvitem{}{Multi-modeling the morphogenesis of transportation networks. In \textit{Artificial Life Conference Proceedings (pp. 382-383). Tokyo, July 2018.}}

\cvitem{}{Modeling Urban Morphogenesis: towards an integration of territories and networks, \textit{GoPro 2017, Lyon, Dec. 2017.}}


\cvitem{}{Complexity, Complexities and Complex Knowledge, \textit{Geodivercity International Workshop, Paris, October 2017.}}


\cvitem{}{Modeling the Co-evolution of Urban Form and Transportation Networks, \textit{Conference on Complex Systems 2017, Cancun, Sept. 2017.}}


\cvitem{}{Raimbault J. \& Baffi S. (2017). Structural Segregation: Assessing the impact of South African Apartheid on Underlying Dynamics of Interactions between Networks and Territories, \textit{ECTQG 2017, York, Sept. 2017}}

\cvitem{}{Invisible Bridges ? Scientific landscapes around similar objects studied from Economics and Geography perspectives, \textit{ECTQG 2017, York, Sept. 2017}}

\cvitem{}{Raimbault, J. \& Bergeaud, A. (2017). The Cost of Transportation: Spatial Analysis of Fuel Prices in the US, \textit{EWGT 2017, Budapest, Sept. 2017}}


\cvitem{}{Cottineau C., Raimbault J., Le Texier M., Le N{\'e}chet F. \& Reuillon R. (2017). Initial spatial conditions in simulation models: the missing leg of sensitivity analyses?, \textit{Geocomputation 2017, Leeds, Sept. 2017}}


\cvitem{}{A macro-scale model of co-evolution for cities and transportation networks, \textit{Medium International Conference, Guangzhou, June 2017}}


\cvitem{}{Losavio C. \& Raimbault J. (2017). Agent-based Modeling of Migrant Workers Residential Dynamics within a Mega-city Region: the Case of Pearl River Delta, China, \textit{Urban China Development International Conference, London, May 2017}}
%
%
%% Pierre-Olivier CHASSET, Hadrien COMMENGES (Géographie-Cités – Université Paris 1), Clémentine COTTINEAU (CASA – University College of London), Christine KOSMOPOULOS (Géographie-Cités – Université Paris 1), Denise PUMAIN (Géographie-Cités – Université Paris 1), Juste RAIMBAULT (LVMT, Université Paris-Est): CybergeoNetworks : un outil interactif pour l’analyse de corpus bibliométriques massifs. Science XXL : Ce que l’abondance et la diversité des données font aux sciences sociales


\cvitem{}{Co-construire Mod{\`e}les, Etudes Empiriques et Th{\'e}ories en G{\'e}ographie Th{\'e}orique et Quantitative: le cas des Interactions entre R{\'e}seaux et Territoires. \textit{Treizi{\`e}mes Rencontres de Th{\'e}oQuant, Besan\c{c}on, May 2017}}


\cvitem{}{Un Cadre de Connaissances pour une G{\'e}ographie Int{\'e}gr{\'e}e. \textit{Journ{\'e}e des jeunes chercheurs de l'Institut de G{\'e}ographie de Paris, Paris, April 2017}}


\cvitem{}{Towards a Theory of Co-evolutive Networked Territorial Systems: Insights from Transportation Governance Modeling in Pearl River Delta, China. \textit{Medium Seminar-Urban Sustainable Development in Zhuhai, Guangzhou, December 2016}}


\cvitem{}{Models of growth for system of cities : Back to the simple, \textit{Conference on Complex Systems 2016, Amsterdam, Sep 2016.}}


\cvitem{}{Raimbault J., Bergeaud A. and Potiron Y. (2016). Investigating Patterns of Technological Innovation. \textit{Conference on Complex Systems 2016, Amsterdam, Sep 2016.}}


\cvitem{}{For a Cautious Use of Big Data and Computation. \textit{Royal Geographical Society - Annual Conference 2016 - Session : Geocomputation, the Next 20 Years (1), London, Aug 2016.}}

\cvitem{}{Indirect Bibliometrics by Complex Network Analysis. \textit{20e Anniversaire de Cybergeo, Paris, May 2016.}}


\cvitem{}{Raimbault, J. \& Serra, H. (2016). Game-based Tools as Media to Transmit Freshwater Ecology Concepts, \textit{poster corner at SETAC 2016, Nantes, May 2016.}}

\cvitem{}{Raimbault, J. (2016). G{\'e}n{\'e}ration de donn{\'e}es Synth{\'e}tiques corr{\'e}l{\'e}es, \textit{Actes des Journ{\'e}es de Rochebrune, January 2016.}}


\cvitem{}{Le Nechet, F. \& Raimbault, J. (2015). Modeling the emergence of metropolitan transport authority in a polycentric urban region, \textit{ECTQG 2015, Bari, Sept. 2015.}}


\cvitem{}{Hybrid Modeling of a Bike-Sharing Transportation System, \textit{poster at ICCSS 2015, Helsinki, June 2015.}}


\cvitem{}{Raimbault, J. \& Gonzales, J. (2015). Application de la Morphog{\'e}n{\`e}se de R{\'e}seaux Biologiques {\`a} la Conception Optimale d'Infrastructures de Transport, \textit{poster presented at Rencontres du Labex Dynamite, Paris, May 2015.}}


%%\cvitem{}{Loeve, S., Raimbault, J. \& al. (june 2014). Student Event, \textit{at Workshop Worldviews and Values in Synthetic Biology,  University Paris 1 Sorbonne, June 6-7, 2014 (http://synenergene.eu/resource/student-event-paris-workshop-worldviews-and-values-synthetic-biology)}.}
%
%%\cvitem{}{When Open Data are Incomplete :
%%Inference of Missing Data for Model Parameterization, \textit{lightning
%%talk at Scientific Open Data Conference (St Mand{\'e}, March 2014)}.}
%
%}
%
%
%
%\full{

\section{Working Papers}




\cvitem{}{Raimbault, J. \& Le Nechet, F. (2018). Closing the loop: Introducing Endogenous Transport Provision in a LUTI Model. \textit{Under review for Journal of Transport Geography.}}


%\cvitem{}{Raimbault, J. (2018). Espace et complexit{\'e}s des syst{\`e}mes territoriaux. \textit{Under review for Rochebrune 2019.}}
% TODO submit

\cvitem{}{Raimbault, J. (2018). Co-evolution and morphogenetic systems. \href{https://arxiv.org/abs/1803.11457}{arxiv:1803.11457}}

\cvitem{}{Raimbault, J. (2018). Reconciling complexities: for a stronger integration of approaches to socio-technical systems. \href{https://arxiv.org/abs/1805.10195}{arxiv:1805.10195}}

%\cvitem{}{Antelope, C., Hubatsch, L., Raimbault, J., and Serna, J. M. (2016). An interdisciplinary approach to morphogenesis. \textit{Working Paper, Santa Fe Institute CSSS 2016.}}

%
%\cvitem{}{Raimbault, J. \& Marandon E. (2016). Optimizing the Extraction of Information from a Complex System.}
%%, \textit{submitted to EPJ Data Science.}}
%
%}
%
%
%
%\full{
%
%
\section{Education}




\cventry{Feb. 2015--Feb. 2018}{PhD in Geography}{G{\'e}ographie-cit{\'e}s (UMR 8504 CNRS) / LVMT (UMR-T 9403 IFSTTAR)}{}{}{Characterizing and Modeling the Co-evolution of Transportation Networks and Territories, \textit{under the supervision of }HDR \textsc{A. BANOS} \textit{and} MCF \textsc{F. LE NECHET}.
}
%\cventry{2015--2018}{PhD in Geography}{G{\'e}ographie-cit{\'e}s (UMR 8504 CNRS) / LVMT (UMR-T 9403 IFSTTAR)}{}{}{Characterizing and Modeling the Co-evolution of Transportation Networks and Territories%, \textit{under the supervision of }HDR \textsc{A. BANOS} \textit{and} MCF \textsc{F. LE NECHET}.
%}


\cventry{June 2016}{SFI Complex Systems Summer School}{Santa Fe Institute}{Santa Fe}{USA}{}



\cventry{2012--2014}{MSc Complex Systems Science}{Ecole Polytechnique ParisTech}{Palaiseau}{France}{Agent-based modeling, Evidence-based methods from Therapeutic Evaluation, Theoretical Analysis of Physical Complex Systems, Epistemology, Complex Networks, Datamining, Signal Processing\\
\textit{Memoire: } Complex Network Analysis for Real-time Trend Detection in a Financial System
}


\cventry{2013--2014}{MSc Urbanism, Environment, Transportation}{Ecole Nationale
des Ponts et Chauss{\'e}es ParisTech}{Marne-la-Vall{\'e}e}{France}{Analysis of Territorial Systems, Management and design of Transportation Systems, Urbanism, History of Urbanism, Urban Economics, Environmental Planning and Design\\
\textit{Memoires:} 
%Application of Evidence-based Methods in Urban Planning and Architecture
Interdisciplinary approaches of modeling and simulations in urban planning and architecture (M1)
; Discrete Choice Models for Bike-sharing Transportation Systems (M2)
}


\cventry{2010--2012}{BSc}{Ecole Polytechnique ParisTech}{Palaiseau}{France}{Multidisciplinary scientific formation (mathematics, computer science, applied mathematics, physics, mecanics, biology, economics)\\
\textit{Research internship in Machine Learning and Artificial Intelligence}: Design and implementation of a matching algorithm
}


%}
%
%
%

\section{Grants and Awards}

\cvitem{}{\textbf{MEDIUM mobility grant}, Young Researcher mobility grant for China, MEDIUM project.% (http://mediumcities-china.org/).%
}

\cvitem{}{\textbf{PhD grant}, \textit{allocation doctorale AMX} for three years from Graduate School, Ecole Polytechnique.}

\cvitem{}{\textbf{Best Student Paper Award} at Conference CSD{\&}M, Paris, December 2014.}

%
%%\newpage
%
%\full{
%
\section{Teaching}


%\cventry{October 2018}{Seminar big data in transportation studies}{Ecole des Ponts et Chauss{\'e}es}{Champs-sur-Marne}{%France
%}{%\textit{Transportation and Mobility Master Seminar}
%}

\cventry{March 2018}{Seminar big data in transportation studies}{Ecole des Ponts et Chauss{\'e}es}{Champs-sur-Marne}{%France
}{%\textit{Transportation and Mobility Master Seminar}
}


\cventry{Spring 2017}{Teaching Assistant}{Universit{\'e} Paris 7}{Paris}{France}{Teaching Assistant: \emph{Statistics and Cartography}, \emph{Spatial Analysis} and \emph{Professionalization for Geographers}.}

\cventry{Feb. 2016}{Seminar Geography and Big Data}{Universit{\'e} Paris 1 Sorbonne}{Paris}{France}{%\textit{G{\'e}oprisme} Master Seminar
}

\cventry{Fall 2015}{Teaching Assistant}{Universit{\'e} Paris 7}{Paris}{France}{Teaching Assistant: \emph{Introduction to Geography} and \emph{Introduction to GIS}.}

%}
%
%
%\full{
%
\section{Reviewing}



\cvitem{since 2019}{Reviewing for \textit{Scientific Reports, Sustainability, International Journal of Geographical Information}}

%\cvitem{since 2018}{Reviewing for \textit{Entropy}}

\cvitem{since 2018}{Reviewing for \textit{Ecological Modeling, Entropy}}

\cvitem{since 2015}{Reviewing for \textit{PLoS ONE}}

\cvitem{since 2015}{Reviewing for \textit{Cybergeo, European Journal of Geography}}

%}
%
%
%\full{
%
\section{Scientific Activity}

\cvitem{2018}{Participation in the CNRS experimental project ``\textit{Incubator for scientific mediation}''}

%
%
%\cvitem{Sept. 2018}{CCS 2018. Satellite Symposium organisation: \textit{New methods and epistemologies to explore simulation models}}
\cvitem{Sept. 2018}{CCS 2018. Satellite organisation: \textit{New methods and epistemologies to explore simulation models}}

%
%
%
%
\cvitem{Sept. 2017}{ECTQG 2017. Session organisation: \textit{Bridges between Economics and Geography: Lessons from Modeling Perspectives
}}

\cvitem{June 2017}{Medium Conference 2017. Session organisation: \textit{Spatio-temporal Behavior in Complex Urban Systems}}

\cvitem{June 2014}{EMCSS Seminar organisation: Comparing Top-down and Bottom-up approaches to Urban Systems}


%
%% Internships are not real positions ; and content already in Memoires in Education
%
%%\section{Research experience}
%%\cventry{Aug.--Dec. 2014}{Research internship}{L2 Technologies}{Paris}{France}{Complex Systems approaches to foreign exchange financial markets}
%
%%\cventry{Sept. 2012\\
%%--Dec. 2013}{Research projects in complex systems science}{}{}{}{Urban planning projects under the supervision of HDR.\noun{ A. Banos }(ISCPIF, Paris)}
%
%%\cventry{April--Sept. 2013}{Research internship}{Chalmers University of Technology, Dpt. of Architecture}{G{\"o}teborg}{Sweden}{Interdisciplinary approaches of modeling and simulations in urban planning and architecture}
%
%%\cventry{July--Sept. 2012}{Research internship}{The Kube SA}{Paris}{France}{Machine Learning and Artificial Intelligence : Design and implementation of an intelligent matching algorithm}
%
%%\cventry{2011--2012}{Collective research project}{Ecole Polytechnique}{}{}{Research project in Image Processing and Machine Learning}
%
%}
%
%
%\full{
%
\section{Computer skills}


\cvcomputer{OS}{Unix (OSX, Ubuntu, CentOS)}{Scripts}{Shell, AppleScript}


\cvcomputer{Programming}{\textsc{Java}, Python, Scala, C/C++, OCaml}{Typography}{\LaTeX{},
API OO.org, ScalaTex}


\cvcomputer{Web}{php, XHTML, CSS, AJAX}{Database}{MySQL, MongoDB, PostgreSQL}


\cvcomputer{Scientific}{R, NetLogo, Gama, OpenMole, Scilab, Matlab, Gephi}{GIS}{QGIS, PostGIS, TransCAD, Ocad}
%
%% Freefem++
%}
%

\section{Languages}

%\cventry{}{French}{Native}{}{}{}
%\cventry{}{German}{Fluent}{European Baccalaureate}{}{}
%\cventry{}{English}{Fluent}{}{}{}
%\cventry{}{Mandarin}{Notions, level HSK1}{}{}{}

\cvcomputer{}{\textbf{French}, \textit{Native}}{}{\textbf{English}, \textit{Fluent}}

\cvcomputer{}{\textbf{German}, \textit{Fluent, European Baccalaureate}}{}{\textbf{Mandarin}, \textit{Notions, level HSK3}}



% Interests is out of scope in an academic CV
%\section{Interests}


%\cvitem{Architecture}{Participation to a draft of an architectural project at the Ecole Polytechnique; courses at ENSAVT; research questions in Architecture during research internship.}

%\cvitem{Orienteering}{4 years (2005-2009) in French National Team ; Member of French Military Team since 2010.}
\end{document}
